---
title: "HW5"
author: "Junyi Ren"
output: github_document
---

```{r}
library(tidyverse)
library(broom)
set.seed(1)
```


## Problem 1
```{r}
homicides = read_csv("./homicide-data.csv")
```

```{r}
homicides_raw_data = homicides |>
  mutate(city_state = paste(city, state, sep=", ")) |>
   group_by(city_state) |>
   summarize(
    Total_Homicides = n(),  
    Unsolved_Homicides = sum(disposition %in% c('Closed without arrest', 'Open/No arrest'), na.rm = TRUE)
  )
```

The homicides raw data consist `r ncol(homicides)` variables and `r nrow(homicides)` observations. Each observation includes uid, reported date, victim first and last name, race, age, sex, city, state, lat, lon, and disposition.

```{r}
Baltimore = homicides |>
   mutate(city_state = paste(city, state, sep=", ")) |>
   group_by(city_state) |>
  filter(city_state == "Baltimore, MD")

prop_test_result =
  prop.test(
  sum(Baltimore$disposition %in% c('Closed without arrest', 'Open/No arrest')),
  nrow(Baltimore))

prop_test_result |>
  broom::tidy() |>
  select(estimate, conf.low, conf.high)
```

```{r}
calculate_prop_test = function(city_data) {
  prop_test_result =
    prop.test(
    sum(city_data %in% c('Closed without arrest', 'Open/No arrest')),
    length(city_data)
  )
  tidy_result =
    broom::tidy(prop_test_result) |>
    select(estimate, conf.low, conf.high)
}

result = homicides |>
    mutate(city_state = paste(city, state, sep=", ")) |>
  group_by(city_state) |>
  summarise(prop_test_results = list(calculate_prop_test(disposition))) |>
  unnest(prop_test_results)
```
```{r}
ggplot(result, aes(y = reorder(city_state, estimate), x = estimate, xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbar(width = 0.2) +
  labs(title = "Estimated and CIs for each city",
       y = "City-State",
       x = "Estimated Proportion") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  coord_flip()
```

## Problem 2

```{r}
longitudinal_study = 
  list.files("data", full.names = TRUE) |>
  enframe(name = "file_name", value = "path") |>
  mutate(
    obs = path |> map(read_csv),
    arm = str_sub(basename(path), 1, 3),
    subject_id = str_remove_all(basename(path), "\\D") |> 
      as.integer()
  ) |>
  unnest(obs) |>
  select(-file_name, -path) |>
  relocate(arm, subject_id, everything()) |>
  pivot_longer(
    cols = starts_with("week_"),
    names_to = "week",
    values_to = "data"
  ) |>
  mutate(week = str_remove(week, "week_")) |>
  mutate(arm = 
           case_match(
             arm,
             "con" ~ "control",
             "exp" ~ "experimental"))

longitudinal_study |>
  ggplot(aes(x = week, y = data, group = subject_id, color = arm)) +
  geom_line() +
  facet_grid(~ arm) +
  labs(title = "Observations Over Time",
       x = "Week",
       y = "Observation") +
  theme_minimal() 
```

From week 1 to week 8, the values of the subjects in the experimental group increased. The values of the control group went up and down with no significant increase or decrease in values


## Problem 3

```{r}
n = 30
sigma = 5
alpha = 0.05
simulations = 5000
mu_values = 0:6

sim_mean = function(n, mu, sigma, simulations) {
  output = vector("list", simulations)
  
  for (i in 1:simulations) {
    data <- rnorm(n, mean = mu, sd = sigma)
    
    t_test_result = t.test(data, mu = 0)
    
    output[[i]] = broom::tidy(t_test_result) |>
      select(estimate, p.value)
  }
  
  do.call(bind_rows, output)
}

results_list = lapply(mu_values, function(mu) {
  sim_mean(n, mu, sigma, simulations) |>
    mutate(true_mu = mu)
})

results_df = bind_rows(results_list)

power_values = results_df |>
  group_by(true_mu) |>
  summarise(power = mean(p.value < alpha))

ggplot(power_values, aes(x = true_mu, y = power)) +
  geom_point() +
  geom_line() +
  labs(title = "Power vs. True Effect Size",
       x = "True Effect Size",
       y = "Power")

```

As the effect size increases, the power increases.

```{r}
avg_estimate_values = results_df |>
  group_by(true_mu) |>
  summarise(avg_estimate = mean(estimate),
            avg_estimate_rej = mean(estimate[p.value < alpha]))


ggplot(avg_estimate_values, aes(x = true_mu, y = avg_estimate, group = 1)) +
  geom_point() +
  geom_line() +
  geom_point(aes(y = avg_estimate_rej), color = "red") +
  labs(title = "Average Estimate vs. True Mean",
       x = "True Mean",
       y = "Average Estimate") 

```


The red line is the average estimate versus the true average. Mean estimates are very close to the true mean. The blue line is the mean estimate of the rejected nulls versus the true mean. When the mean is 0, 1, 2, 3, and 4, the sample means of the rejected nulls are not approximately equal to the true value of the mean because the power is not large enough. As the power increases or the effect size increases, the sample mean estimate will be very close to the mean.
